//The functionality requirement for student's user interface are login/register at startup page, showing course list elected by student, showing selected course content, homework/assignment submission, checking grade and survey associate to that course.//(changes are followed up, Do not delete)


\subsection{Login and Register}
//From the users' points of view, this page shall be simple and focused with only username/email, password and forget option just as many other web page. Along with the register link that would lead user to a different page to complete registration process. The registration process would require back end to send verification code through email or text to verify the user. After matching the verification code with the users' input, the password is finally able to be reset. //(Do not delete this section, apply to report later)


As a student, I want to have the login process to be done in a fast response time so that it does not require a lot of time to wait. As a matter of fact, the more that I expect for in this section is about the security matters. So that, to avoid any inconvenient operations, if I accidentally forget my login password, I am still able to find it back and reset at this step.
\subsection{Course List}
//This page would show all the courses that the user registered for. The list of courses for the user will be presented on the page right after the login operation from the user. The On-Load function will be executed as soon as the page is being loaded. During the loading process of this page, a request from the front-end will be sent to the server with required parameters. In response to that, the serve will send back the course list of the user and then which will be able to view on the page. //(Do not delete this section, report template)


As a student, I want to have all my personal information manageable and related academic information easy to approach on the interface so that I am able to make my work much easier through the interface. To reach my basic purpose and demand, it is also necessary to have a quick response time so that I am also able to review the most recent updates from my teachers.

\subsection{Course Content}
As a student, I want to be able to view all the content of courses that I registered for. So that my academic information can be easily accessed through the interface. 

\subsection{Homework and Assignment Submission}
As a student, one of the biggest purposes that I am using this software is to make faster and easier homework submissions online. Therefore, I want to be able to view each homework requirements posted by teachers and make submissions by text, voice message and pictures. 

\subsection{Checking Grade and Feedback}
As a student, I want to know the grade for my assignment, quiz and exam as soon as teacher posted. So that the grade and feedback of my work can be checked online easier and faster. I will also be able to correct my mistake and learn from it sooner. 

\subsection{Survey}
As a student, I want to have a survey section on the interface so that I will be able to put on feed-backs for each courses for future improvements. 

